Metrics

### 2023-12-06 src/metrics.Rmd
Adjust plot dims
Clean up labels to disp values only if more than one model

@@

# Prepare boxplot data
coddata <- out %>%
    select(
        Model,
        starts_with("PCCC COD Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC COD Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "COD",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "COD" = recode(`COD`, !!!cod_remap)
    ) %>%
    group_by(`COD`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
    )

@@

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_dotplot(
        binaxis = "y",
        binwidth = 0.03,
        dotsize = 0.3,
        fill = "white",
        color = "darkgray",
        stackdir = "center",
        stackratio = 2,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        position = position_nudge(y = 0.055, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.1, 0.75) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

@@

@@

# Prepare boxplot data
ardata <- out %>%
    select(
        Model,
        starts_with("PCCC Age Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC Age Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Age Range",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "Age Range" = recode(`Age Range`, !!!arange_remap)
    ) %>%
    group_by(`Age Range`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
    )

@@

# Plot boxplot
arplot <- ardata %>%
    ggplot(aes(x = `Age Range`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2.5,
        hjust = 1,
        position = position_nudge(y = -0.12)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2.5,
        hjust = 0,
        position = position_nudge(y = 0.12)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.06),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.06),
        size = 3
    ) +
    labs(
        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(-0.3, 1.3) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_blank(),
        axis.line.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            color = "black",
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        )
    )

>>>>

```{r, fig.height = 4, fig.width = 6}

@@

# Prepare boxplot data
coddata <- out %>%
    select(
        Model,
        starts_with("PCCC COD Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC COD Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "COD",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "COD" = recode(`COD`, !!!cod_remap)
    ) %>%
    group_by(`COD`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) * 1.03,
            paste0(Model, " (", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) * 0.97,
            paste0(Model, " (", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                       collapse = "\n")
            ),
            NA
        )
    )

@@

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_dotplot(
        binaxis = "y",
        binwidth = 0.03,
        dotsize = 0.3,
        fill = "white",
        color = "darkgray",
        stackdir = "center",
        stackratio = 2,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        position = position_nudge(y = 0.055, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.2, 0.8) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

@@

```{r, fig.height = 11, fig.width = 8}

@@

# Prepare boxplot data
ardata <- out %>%
    select(
        Model,
        starts_with("PCCC Age Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC Age Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Age Range",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "Age Range" = recode(`Age Range`, !!!arange_remap)
    ) %>%
    group_by(`Age Range`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) * 1.03,
            paste0(Model, " (", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) * 0.97,
            paste0(Model, " (", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                       collapse = "\n")
            ),
            NA
        )
    )

@@

# Plot boxplot
arplot <- ardata %>%
    ggplot(aes(x = `Age Range`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2.5,
        hjust = 1,
        position = position_nudge(y = -0.065)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2.5,
        hjust = 0,
        position = position_nudge(y = 0.065)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.03),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.03),
        size = 3
    ) +
    labs(
        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.1, 1) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_blank(),
        axis.line.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            color = "black",
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        )
    )
